 

### 2021-07-13 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

There are, however, noteable exceptions to this pattern: in eight mesic forests across the northeast United States, growth rates of understory trees declined sharply at higher $T_{air}$ [Fig `r fig_treerings` **???**; @rollinsonClimateSensitivityUnderstory].
Similarly, in tropical forests higher night-time temperatures have been associated with decelerating tree growth rates predominantly in smaller trees *but also in taller trees* [*Clark 2010; 2013; Feeley et al. 2007*].
Potential mechanisms for these patterns include increases in nighttime respiratory carbon loss that disproportionately reduced carbon availability for growth among small trees, or that understory $g_s$  might be stifled under humid conditions, resulting in higher $T_{leaf}$ (Fig. `r fig_leaf_T`) and lower photosynthesis. 
It is also possible that higher temperatures reduce understorty tree growth in these forests through an indirect mechanism, such as accelerated competition under warmer temperatures. 
Additional research is required to understand these mechanisms and to disentangle tree growth responses to hot-wet versus hot-dry conditions.

>>>>

There are, however, noteable exceptions to the pattern of greater growth reductions under high $T_{air}$ among larger trees.
In eight mesic forests across the northeast United States, tree-ring records showed steep growth declines of understory trees at higher $T_{air}$, contrasting with the responses of canopy trees [Fig `r fig_treerings`, @rollinsonClimateSensitivityUnderstory].
Similarly, in tropical forests higher night-time temperatures have been associated with decelerating tree growth rates predominantly in smaller trees *but also in taller trees* [*Clark 2010; 2013; Feeley et al. 2007*].
Potential mechanisms for these patterns include increases in nighttime respiratory carbon loss that disproportionately reduced carbon availability for growth among small trees, or that understory $g_s$  might be stifled under humid conditions, resulting in higher $T_{leaf}$ (Fig. `r fig_leaf_T`) and lower photosynthesis. 
It is also possible that higher temperatures reduce understorty tree growth in these forests through an indirect mechanism, such as accelerated competition under warmer temperatures. 
Additional research is required to understand these mechanisms and to disentangle tree growth responses to hot-wet versus hot-dry conditions.
